%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

\cvsubsection{Oral Presentations}
\vspace{-6mm}
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Degree
    {} % Institution
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
\item \textit{Joint Statistical Meetings, 2018}. Degree centrality of SNPs in eQTL networks.
\item \textit{ENAR Spring Meeting, 2017}. Error quantification in biologically relevant eQTL network metrics.
\item \textit{Massachusetts General Hospital Trauma Genomics Group, 2017}. Mediation analysis of pathways to PTSD diagnosis.
\item \textit{Broad Institute Statistical Genetics Seminar, 2017}. Causal mediation analysis for genomic data.
\item \textit{Biostatistics Student Seminar, 2016}. Graduate Research Fellowships.
\item \textit{Joint Statistical Meetings, 2016}. Genomic analysis with common binary outcomes via mediation.
\item \textit{ENAR Spring Meeting, 2016}. Mediation methods for case-control settings with applications to genomics.
\item \textit{Harvard Medical School Epigenetics Symposium, 2015}. Integrating epigenetic and genomic analyses via mediation analysis.
\item \textit{Joint Statistical Meetings, 2015}. Mediation-based integrative genomic analysis.
\item \textit{Biostatistics Student Seminar, 2015}. A mediation-based integrative genomic analysis of lung cancer.
\item \textit{ENAR Spring Meeting, 2015}. Mediation-based integrative genomic analysis.
\item \textit{International Association for Dental Research Epi-Forum, 2015}. Preweighted sparse clustering with applications to temporomandibular disorder.
\item \textit{ENAR Spring Meeting, 2014}. Identification of biologically relevant subtypes via preweighted sparse clustering.
      \end{cvitems}
    }
\end{cventries}

\cvsubsection{Poster Presentations}
\vspace{-6mm}

\begin{cventries}
    
    \cventry
    {} % Degree
    {} % Institution
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
\item \textit{ENAR Spring Meeting, 2018}. Assessing the Effective Degree of SNPs in eQTL Networks. Oral poster.
\item \textit{American Society for Human Genetics Annual Meeting,  2016}. Mediation methods applied to post-traumatic stress disorder to identify genomic effects.
\item \textit{Harvard Graduate Women in Science and Engineering Symposium,  2015}. A mediation-based integrative genomic analysis of lung cancer.
\item \textit{UNC Celebration of Undergraduate Research,  2013}. The association between oral contraceptive use and painful conditions.
\item \textit{International Pelvic Pain Society Conference,  2012}. OPPERA Study Identifies an Association Between the Use of Hormonal Contraceptives and Orofacial Pain and Headaches. Prepared poster, First place in poster competition.
\item \textit{ENAR Spring Meeting, 2012}. Identification of clinically relevant disease subtypes using supervised sparse clustering.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
