%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvpapers}

%---------------------------------------------------------

\cvpaper
{\textbf{Gaynor, S.M.}, Fillingim, R.B., Zolnoun, D.A., Slade, G.D., ... \& Bair, E. (2021). Association between craniofacial pain and hormonal contraceptive use: The OPPERA study. \textit{Journal of Oral \& Facial Pain and Headache}.} % Award
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
{\textbf{Gaynor, S.M.}, Bortsov, A.V., Bair, E., Fillingim, R.B., ... \& Smith, S. (2021). Phenotypic profile clustering pragmatically identifies diagnostically and mechanistically informative subgroups of chronic pain patients. \textit{PAIN}.} % Award
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
{Sun, R., Xu, M., Li, X., \textbf{Gaynor, S.}, ... \& Lin, X. (2021). Integration of multiomic annotation data to prioritize and characterize inflammation and immune-related risk variants in squamous cell lung cancer. Genetic epidemiology, 45(1), 99-114.}
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
{Raffield, L.M., Iyengar, A.K., Wang, B., \textbf{Gaynor, S.M.}, ... \& Auer, P.L. (2020). Allelic Heterogeneity at the CRP Locus Identified by Whole-Genome Sequencing in Multi-ancestry Cohorts. \textit{American Journal of Human Genetics}, 106(1), 112-120.} % Award
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
{Li, X.*, Li, Z.*, Zhou, H., \textbf{Gaynor, S.M.}, ... \& Lin, X. (2020). Dynamic incorporation of multiple in silico functional annotations empowers rare variant association analysis of large whole-genome sequencing studies at scale. Nature genetics, 52(9), 969-983.}
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
{\textbf{Gaynor, S.M.}*, Sun, R.*, Lin, X, \& Quackenbush, J. (2019). Identification of differentially expressed gene sets using the Generalized Berk-Jones statistic. \textit{Bioinformatics}.} % Award
{} % Event
{ } % Location
{} % Date(s)

\cvpaper
    {\textbf{Gaynor, S.M.}, Schwartz, J., \& Lin, X. (2019). Mediation analysis for common binary outcomes. \textit{Statistics in Medicine}, 38(4), 512-529.} % Award
    {} % Event
    { } % Location
    {} % Date(s)
    
    \cvpaper
    {Borrelli, B., \textbf{Gaynor, S.}, Tooley, E., Armitage, C.J., Wearden, A., \& Bartlett, Y.K. (2018). Identification of three different types of smokers who are not motivated to quit: Results from a latent class analysis. \textit{Health Psychology}, 37(2), 179.} % Award
    {} % Event
    { } % Location
    {} % Date(s)
    
    
  \cvpaper
    {\textbf{Gaynor, S.}, \& Bair, E. (2017). Identification of relevant subtypes via preweighted sparse clustering. \textit{Computational Statistics \& Data Analysis}, 116, 139-154.} % Award
    {} % Event
    { } % Location
    {} % Date(s)
    
 \cvpaper
    {Bair, E., \textbf{Gaynor, S.}, Slade, G.D., Ohrbach, R., Fillingim, R.B., Greenspan, J.D., ... \& Maixner, W. (2016). Identification of clusters of individuals relevant to temporomandibular disorders and other chronic pain conditions: the OPPERA study. \textit{Pain}, 157(6), 1266.} % Award
    {} % Event
    { } % Location
    {} % Date(s)
    
    
\end{cvpapers}

Under Review and Preprints

\begin{cvpapers}
	
		\cvpaper
	{{Shi, A.}*, \textbf{Gaynor, S.M.}*, Quick, C., and Lin, X. Multi-resolution characterization of the COVID-19 pandemic: A unified framework and open-source tool. medRxiv [Preprint]. March 13, 2021. Available from: https://doi.org/10.1101/2021.03.12.21253496.} % Award
	{} % Event
	{ } % Location
	{} % Date(s)
	
	\cvpaper
	{\textbf{Gaynor, S.M.}*, DiCorpo, D.*, Westerman, K., Russell, E., ... \& Manning, A. Whole Genome Sequence Association Analysis of Fasting Glucose and Fasting Insulin Levels in Diverse Cohorts from the NHLBI TOPMed Program. medRxiv [Preprint]. January 4, 2021. Available from: https://doi.org/10.1101/2020.12.31.20234310.} % Award
	{} % Event
	{ } % Location
	{} % Date(s)
	
	\cvpaper
	{Li, D., \textbf{Gaynor, S.M.}, Quick, C., Chen, J. T., ... \& Lin, X. Identifying US Counties with High Cumulative COVID-19 Burden and Their Characteristics. medRxiv [Preprint]. January 12, 2021. Available from: https://doi.org/10.1101/2020.12.02.20234989.} % Award
		{} % Event
	{ } % Location
	{} % Date(s)
	
	\cvpaper
	{McCaw, Z.R., \textbf{Gaynor, S.M.}, Sun, R.,  and Lin, X. Cross-tissue eQTL Calling via Surrogate Expression Analysis.} % Award
	{} % Event
	{ } % Location
	{} % Date(s)
	
	\cvpaper
	{\textbf{Gaynor, S.M.}, Fagny, M., Lin, X., Platig, J., Quackenbush, J. Connectivity of variants in eQTL networks dictates reproducibility and functionality. bioRxiv 515551 [Preprint]. January 9, 2019. Available from: https://doi.org/10.1101/515551.} % Award
	{} % Event
	{ } % Location
	{} % Date(s)
	
	\cvpaper
	{\textbf{Gaynor, S.M.}, Lin, X., Quackenbush, J. Spectral clustering in regression-based biological networks. bioRxiv 651950 [Preprint]. May 27, 2019. Available from: https://doi.org/10.1101/651950.} % Award
	{} % Event
	{ } % Location
	{} % Date(s)
	
	
	
\end{cvpapers}